% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Zhang Mengxiang}

\basicInfo{
  \email{coderzmx@zju.edu.cn} \textperiodcentered\ 
  \phone{(+86) 137-039-22842} \textperiodcentered\ 
  }

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Zhejiang University (ZJU)}, Hangzhou, China}{2020 -- Present}
\textit{Master student} in Software Engineering (SE), expected March 2023
\datedsubsection{\textbf{Nanchang University}, Nanchang, China}{2016 -- 2020}
\textit{B.S.} in Software Engineering (SE)

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Institute of Computer Innovation of ZJU} Hangzhou, China}{Jan.2022 -- Jun.2022}
\role{Daily Intern}{Algorithm Engineering in AI-powered Universal Platform}
Participate in the development of algorithms in sports monitoring projects
\begin{itemize}
  \item Participate in the optimization of some algorithms
  \item Using Algorithm to Realize Automatic Counting Function of Sports
\end{itemize}

\datedsubsection{\textbf{Didi Chuxing Technology Co., Ltd}}{Jun.2021 -- Dec.2021}
\role{Daily Intern}{Backend Software Engineer in Merchant Management Department}
Participate in the development of Xiaojuchefu-Merchant system
\begin{itemize}
  \item Upgrades to the merchant onboarding process
  \item Rating of merchants
  \item Home Page Revision of Merchant system
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Proficiency in Java language, familiar with the use of collection classes, JVM principles, and understanding of multi-threaded programming.
  \item Familiar with Spring boot, Mybatis, Dubbo and other common frameworks.
  \item Proficiency in Mysql, familiar with the principles of database systems, understanding of MYSQL indexes and storage engines.
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{National Second Prize of Blue Bridge Cup Programming Competition}{Apr. 2019}
\datedline{Nanchang University Special Scholarship}{Oct. 2019}
\datedline{National Inspirational Scholarship}{Jun. 2017}

\section{\faProjectDiagram\ Projects}
\textbf{MyRpc}


   Implementing RPC framework from scratch using Netty+Kryo+Zookeeper.The main functions include service registration, service discovery, remote procedure invocation, load balancing, network transfer, etc.
   
   
\textbf{Online Bookstore}


   The project is divided into two modules, foreground System and background system. The foreground System mainly serves for users, providing functions such as browsing, purchasing books, posting comments, viewing orders and maintaining personal information. The backend mainly provides some management functions and Permission Control.

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
